\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color} 
\usepackage{titling}

\title{\vspace*{\fill} My DropBox}
\author{
	Faran Ahmad\\
	2013CS10220
	\and
	Kartikeya Gupta\\ 
	2013CS10231
	\and
	Prateek Kumar Verma\\ 
	2013CS10246
}
\date{COP290: Design Practices \vspace*{\fill}}

\begin{document}
	\maketitle

	\newpage

	\section{Objectives}
	We have to build an online file management system \" MyDropBox \". A server machine maintains the files of multiple users. The user should use a simple desktop application to login into the system. The content of user's account should remain synced with the server. 

	\section{Overall Design}
		\begin{enumerate}
			\item We will begin with creating different sub components like a File Transferring System, Credential Verifier, GUI part.
			\item Once the components are ready, we will Link this to the network and get basic functionality working on the localhost.
			\item Once the local interface is ready, we will take this to the web portal. We will use a server to store data and users will have to send queries to it
			\item Once the web portal is ready we will link the offline and online parts.
		\end{enumerate}

	\section{Sub Components}
		\begin{enumerate}
			\lstset{
				frame=tb, % draw a frame at the top and bottom of the code block
			   	tabsize=4, % tab space width
			   	showstringspaces=false, % don't mark spaces in strings
			    numbers=left, % display line numbers on the left
			    commentstyle=\color{red}, % comment color
			    keywordstyle=\color{blue}, % keyword color
			    stringstyle=\color{green} % string color
			}
			\item \textbf{User Verification}
			\begin{lstlisting}[language=C++, caption={Class Parameters for User}]
class User
{
	private:
		std::string UserName;
		std::string PassWord;	
};
			\end{lstlisting}
			\begin{lstlisting}[language=C++, caption={Class Parameters for User}]
class UserBase
{
private:
	std::unordered_map<std::string, std::string> UsersList;
};
			\end{lstlisting}
			The User Base is a hastable in which the keys are usernames and the stored values are passwords. When the credentials of the user are to be verified, the key is looked up in the table. Inserting users is also achieved easily using this model.
			
			\item \textbf{GUI interface} 
				\newline
				TODO: FARAN
			\item \textbf{Network Managing Part}
			\item \textbf{Data Syncing Part}
				\newline
				\begin{lstlisting}[language=C++, caption={Class Parameters for File History}]
class FileHistory
{
	private:
		std::string FolderLocation;
		std::vector< std::pair<std::string, int> > FileTimeBase;
};
			\end{lstlisting}
			

		\end{enumerate}
	\section{Integration amongst Sub Components}

	\section{Testing}
		\begin{enumerate}
			\item Offline Testing
			\item Online Testing
		\end{enumerate}

	\section{Extra Features}

\end{document}
